\section*{БИБЛИОГРАФИЧЕСКИЙ СПИСОК}
\addcontentsline{toc}{section}{Библиографический список}

\subsection*{Список использованных источников}
\addcontentsline{toc}{subsection}{Список использованных источников}

\begingroup

\renewcommand{\section}[2]{}

\begin{thebibliography}{}

\bibitem{moluch}
Сагиндыкова А. С., Тугамбекова М. А.
Актуальность дистанционного образования // Молодой ученый. — 2015. — №20. — С. 495-498.
[Электронный ресурс]. – Режим доступа:
\href{https://moluch.ru/archive/100/20703/}{https://moluch.ru/archive/100/20703/}
(дата обращения: 05.01.2019).

\bibitem{the-steppe}
  10 онлайн-платформ, которые прокачают ваш мозг.
  [Электронный ресурс]. – Режим доступа:
  \href{https://the-steppe.com/news/gorod/2018-05-18/10-onlayn-platform-kotorye-prokachayut-vash-mozg}{https://the-steppe.com/news/gorod/2018-05-18/10-onlayn-platform-kotorye-prokachayut-vash-mozg}
  (дата обращения: 05.01.2019).

\bibitem{udacity}
  Udacity - Википедия. [Электронный ресурс]. – Режим доступа:
  \href{https://ru.wikipedia.org/wiki/Udacity}{https://ru.wikipedia.org/wiki/Udacity}
  (дата обращения: 05.01.2019).

\bibitem{docker}
  Docker - Википедия. [Электронный ресурс]. – Режим доступа:
  \href{https://ru.wikipedia.org/wiki/Docker}{https://ru.wikipedia.org/wiki/Docker}
  (дата обращения: 09.01.2019).

\bibitem{angular}
  10 преимуществ использования фреймворка Angular.js при разработке веб-приложений [Электронный ресурс]. – Режим доступа:
  \href{https://stfalcon.com/ru/blog/post/why-use-angularjs-for-webapps}{https://stfalcon.com/ru/blog/post/why-use-angularjs-for-webapps}
  (дата обращения: 09.01.2019).



\bibitem{}
  Paul Barry
  \emph Head-First Python, 2nd edition,
  O’Reilly,
  2016.

\bibitem{}
  Andi Gutmans, Stig Sæther Bakken, and Derick Rethans,
  \emph Learning Python, 5th Edition,
  O’Reilly,
  2013.

\bibitem{}
  Regina O. Obe, Leo S. Hsu
  \emph PostgreSQL: Up and Running: A Practical Guide to the Advanced Open Source Database
  O'Reilly Media; 3 edition (October 30, 2017).

\bibitem{}
  Hans-Jurgen Schonig,
  Troubleshooting PostgreSQL,
  Packt Publishing - ebooks Account (March 31, 2015).

\bibitem{}
  Bharvi Dixit,
  Elasticsearch Essentials,
  Packt Publishing - ebooks Account (January 30, 2016).

\bibitem{}
  William S. Vincent,
  REST APIs with Django: Build powerful web APIs with Python and Django,
  Independently published (June 15, 2018).

\bibitem{}
  Baron Schwartz, Peter Zaitsev, Vadim Tkachenko, Jeremy Zawodny, Arjen Lentz, Derek J. Balling,
  Django 2 Web Development Cookbook: 100 practical recipes on building scalable Python web apps with Django 2, 3rd Edition,
  O'Reilly Media (2008).


\bibitem{}
  Paul DuBois,
  MySQL Cookbook,
  O'Reilly Media (2006)

\bibitem{}
  Charles Bell, Mats Kindahl, Lars Thalmann,
  MySQL High Availability: Tools for Building Robust Data Centers,
  O'Reilly Media (2010)

\bibitem{}
  Michael Kruckenberg, Jay Pipes,
  Pro MySQL (The Expert's Voice in Open Source),
  Apress Media (2005)

\bibitem{}
  Seyed Tahaghoghi, Hugh Williams,
  Learning MySQL,
  O'Reilly Media (2006)

\bibitem{mihnuk07}
  Christian Nwamba,
  TypeScript 2.x for Angular Developers: Harness the capabilities of TypeScript to build cutting-edge web apps with Angular,
  Packt Publishing - ebooks Account (December 7, 2017).

\bibitem{devisilov09}
  Adam Freeman,
  Pro Angular 6,
  Apress; 3rd ed. edition (October 10, 2018).

\bibitem{belov09}
  Jeremy Wilken,
  Angular in Action.
  Manning Publications; 1 edition (April 2, 2018).

\bibitem{decree432}
  Gabriel N. Schenker,
  Learn Docker - Fundamentals of Docker 18.x: Everything you need to know about containerizing your applications and running them in production,
  Packt Publishing (April 26, 2018).

\bibitem{palitsyn06}
  Gigi Sayfan,
  Mastering Kubernetes: Master the art of container management by using the power of Kubernetes, 2nd Edition,
  Packt Publishing; 2nd Revised edition edition (April 27, 2018).

\bibitem{palitsyn06}
  Jeeva S. Chelladhurai, Vinod Singh, Pethuru Raj,
  Learning Docker - Second Edition: Build, ship, and scale faster,
  Packt Publishing - ebooks Account; 2nd Revised edition edition (May 31, 2017).

\end{thebibliography}

\subsection*{Список публикаций соискателя}
\addcontentsline{toc}{subsection}{Список публикаций соискателя}

\begin{thebibliography}{}

\bibitem{}
  Теслюк В.Н., Танасюк О.О.
  Разработка образовательной платформы для хранения, обработки, просмотра видеоматериалов
  // Студенческий форум: электрон. научн. журн. 2019. № 1(52).
  [Электронный ресурс]. – Режим доступа:
  \href{https://nauchforum.ru/journal/stud/52/45530}{https://nauchforum.ru/journal/stud/52/45530}
  (дата обращения: 05.01.2019).

\end{thebibliography}{}

\endgroup